---
title       : Interactive Class Apps
subtitle    : Guided Experiment Learning
author      : Imaginary Products
job         : Next Step in Education
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # tomorrow, zenburn
widgets     : [mathjax, bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Learning Data Science

Science is how we attempt to understand and manipulate the world around us. There is always data, relations, questions, algorithms and insight. Take for example a set of cars.

```{r, echo=FALSE, fig.height=5, fig.width=6, fig.pos= 'H'}
  data(mtcars)
  model <- lm(mpg ~ wt, mtcars)
  # Plotting Elements
  plot(mpg ~ wt, mtcars,
       col = 'blue', pch = 16, lwd = 3,
       #xlim = c(lowerX,higherX), ylim = c(lowerY,higherY),
       xlab = 'Weight (lbs/1000)', ylab = 'MPG', main = 'Miles per Gallon ~ Weight')
  abline(model, col = 'green', lwd = 5)
  legend('topright', c('Studied Cars','Linear Model'), pch = 16, col = c('blue','green'))
```

You can see how the car weight influences it's miles per gallon performance. Data analysis can help you understand further! **But first you must learn theory and practice!**

--- .class #id  &twocol w1:40% w2:60%

## Learning Experience MATTERS!

Consider a class on linear models

$$\Large Y = \sum_{i=1}^{n}{\beta_iX_i}$$

They are very interesting, but the learning experience depends on the resources available to the student, the professor or mentor and the learning traits.

*** {name: left}
### Offline Class

- Face to face with professor and peers
- Questions solved on the spot
- Lots of **Guided Manual Exercises**
- **Immediate feedback**
- Student mistakes are corrected immediatly

*** {name: right}
### Online Class
- Massive **online resources**
- Flexible class schedules (learn at your pace)
- Student is **free to explore**
- Feedback has a delay
- Errors or mispractice is not identified quickly

--- .class #id

## Our Idea Pitch

Inspired by resources like `manipulate` and `swirl` R packages and [W3Schools](http://www.w3schools.com/), we at IP believe that under a controlled scenario a student can learn in an app that merges exercises with scenario exploration, explanations and data interpretation.

Take a moment to visit our [first webapp](https://csmc88.shinyapps.io/shinyClass). It is both a class and a guided exercise on the topic of extrapolating with linear models. 

```{r Possibility2}
data(mtcars)
fit <- lm(mpg ~ wt, mtcars)
summary(fit)$coefficients
```

Simple OLS is easy to understand, but it is far more educative to study it by playing with data and a mentor close by.

--- .class #id &checkbox

## Think of the possibilities

Our first app might seem a little raw and incomplete. But the *IDEA* can be taken further as an additional resource for online courses or a class all in itself. 

With additional work, the app can even teach R programming! Through interactive plots and controlled R code these **online guided experiments** can help a student learn the development and modeling concepts of data science.

### What do you think?   
1. _I want to give feedback on this_
2. _New teaching resources are always welcome_
3. _This should be done carefully_
4. This won't work

*** .hint
Don't be negative, try new things and fail quickly to learn faster. 
*** .explanation
Thank you! We believe in open ideas developed with care and teamwork!.  
